Syntax Is All You Need: A Universal-Language Approach to Mutant Generation

### 2023-03-29 paper/main.tex
fixed up java table.

\begin{table}[htbp]
\centering
{\small
\caption{Java (Our Implementation vs. PIT vs. LittleDarwin)}
\label{tab:table_java2}
\begin{tabularx}{\columnwidth}{l|rrr|rrr|rrr}
\hline
                 & \mc{3}{c|}{Comby}   & \mc{3}{c|}{PIT} & \mc{3}{c}{LittleDarwin} \\
\textbf{Project} & \textbf{Mutants} &  \makecell{\textbf{Mutation} \\ \textbf{Score}} & \textbf{\% Eqv}
& \textbf{Mutants} &  \makecell{\textbf{Mutation} \\ \textbf{Score}} & \textbf{\% Eqv} 
& \textbf{Mutants} &  \makecell{\textbf{Mutation} \\ \textbf{Score}} & \textbf{\% Eqv} \\ \midrule

pebble & 85 & 0.81 & 20\% & 20 & 0.95 & N/A & 8 & 1.00 & 0\% \\
spring-hateoas & 176 & 0.37 & 0\% & 114 & 0.28 & N/A & 38 & 0.39 & 0\% \\
javacc & 503 & 0.21 & 0\% & 143 & 0.21 & N/A & 82 & 0.78 & 0\% \\
coffee-gb & 174 & 0.23 & 0\% & 36 & 0.89 & N/A & 29 & 0.38 & 0\% \\
egads & 622 & 0.71 & 10\% & 107 & 0.81 & N/A & 85 & 0.87 & 0\% \\
apk-parser & 338 & 0.08 & 0\% & 89 & 0.16 & N/A & 33 & 0.09 & 0\% \\
\midrule
\textbf{Mean} &  316.33 & 0.40 & 5.00\% & 84.83 & 0.55 & N/A & 45.83 & 0.59 & 0.00\% \\
\textbf{Std.Dev.} &  210.81 & 0.29 & 8.37\% & 47.60 & 0.37 & N/A & 30.93 & 0.35 & 0.00\%8
 \\
\end{tabularx}
}
\end{table}

>>>>

\begin{table}[htbp]
\centering
\caption{Java (Our Implementation vs. PIT vs. LittleDarwin). \claire{FIXME: explain why no eqv for PIT.} LittleDarwin produces no equivalent mutants.\claire{right?}}
\label{tab:table_java2}
\resizebox{\columnwidth}{!}{% again don't love it, but footnotesize is actually smaller than necessary here
\begin{tabular}{l|rrr|rr|rr}
\toprule
                 & \mc{3}{c|}{\textbf{Comby}}   & \mc{2}{c|}{\textbf{PIT}} & \mc{2}{c}{\textbf{LittleDarwin}} \\
\textbf{Project} & \textbf{Muts.} &  \makecell{\textbf{Mut.} \\ \textbf{Score}} & \textbf{\% Eqv}
& \textbf{Muts.} &  \makecell{\textbf{Mut.} \\ \textbf{Score}}
& \textbf{Muts.} &  \makecell{\textbf{Mut.} \\ \textbf{Score}} \\ \midrule

pebble & 85 & 0.81 & 20\% & 20 & 0.95  & 8 & 1.00  \\
spring- & \mr{2}{176} & \mr{2}{0.37} & \mr{2}{0\%} & \mr{2}{114} & \mr{2}{0.28}  & \mr{2}{38} & \mr{2}{0.39}  \\
hateoas  &    &       &     &    &   &   &   \\[0.5ex]
javacc & 503 & 0.21 & 0\% & 143 & 0.21  & 82 & 0.78  \\
coffee-gb & 174 & 0.23 & 0\% & 36 & 0.89 & 29 & 0.38  \\
egads & 622 & 0.71 & 10\% & 107 & 0.81  & 85 & 0.87  \\
apk-parser & 338 & 0.08 & 0\% & 89 & 0.16  & 33 & 0.09 \\
\midrule
\textbf{Mean} &  316.33 & 0.40 & 5.00\% & 84.83 & 0.55  & 45.83 & 0.59  \\
\textbf{Std.Dev.} &  210.81 & 0.29 & 8.37\% & 47.60 & 0.37 & 30.93 & 0.35 \\\bottomrule
\end{tabular}
}
\end{table}
